---
title: "xflyr_vignette"
author: Jane Wall
date: November 21, 2019
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{xflyr_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE, warning = FALSE}
library(xflyr)
#library(tidyverse)
```

xflyr contains functions to scrape data from the cross country paragliding website, <https://www.xcontest.org/world/en/pilots/>.  The top-level function xc_summary() reads in the pilot data from all the pages of the website and puts the pilot info together in one large dataset.

```{r get_data}
pilot_data <- xc_summary()
head(pilot_data)
nick_data <- pilot_data$nickname
head(nick_data)
```

I plan to build additional functions that scrape the detailed data for each pilot from the detail website and put that data together into a nested list for analysis purposes.
